Modeling potential JCPOA diversion scenarios using Cyclus

### 2018-01-27 paper.tex
...
1 typo + formating

The tuning method outlined here does not re-optimize $\theta_i$ based on the
true flow enrichment. As $\delta U$ and $\alpha$ do not depend on the stage feed
assay ($N'$), they do not change from stage to
stage. According to equation \eqref{eq:beta}, when $\alpha$ and $\theta$ are
fixed, whenthe feed assay ($N$) changes, then $\beta$ will change accordingly.
This breaks the ideal status of the cascade, i.e.  $N_{i} \neq N'_{i-1} \neq
N''_{i+1}$.

@@

Case 2 is also limited to 30 cascades in the scenario (the maximum allowable under
the JCPOA agreement), but this time each level of cascades are optimized for the feed they recieve from the previous level's product. Each cascade has 4 stripping stages and
10 enriching stages.

>>>>

The tuning method outlined here does not re-optimize $\theta_i$ based on the
true flow enrichment. As $\delta U$ and $\alpha$ do not depend on the stage feed
assay ($N'$), they do not change from stage to
stage. According to equation \eqref{eq:beta}, when $\alpha$ and $\theta$ are
fixed, when the feed assay ($N$) changes, then $\beta$ will change accordingly.
This breaks the ideal status of the cascade, i.e.  $N_{i} \neq N'_{i-1} \neq
N''_{i+1}$.

@@

Case 2 is also limited to 30 cascades in the scenario (the maximum allowable
under the JCPOA agreement), but this time each level of cascades are optimized
for the feed they receive from the previous level's product. Each cascade has 4
stripping stages and 10 enriching stages.
